---
title: "Learn Plotting"
author: "SamuelChan"
date: "4/18/2020"
output: html_document
---

## My Exercise

`summary` prints a summary of the dataset, which gives me information on the minimum, maximum, the different quantiles and the average (mean): 

```{r cars}
summary(cars)
```
I can use `max()` to obtain the maximum value in my data:

```{r maxvalue}
maxv <- max(cars)
print(maxv)
```

The maximum value in our data is `r maxv`.

```{r experiment}
# sample 5 numbers from 1 to 120
sample(1:maxv, 5)
```

```{python lists}
# create a list
list(i*2 for i in [2,4,6])
```


## Including Plots
`volcano` is another built-in dataset, and we can use the `image()` function to create a colored grid corresponding to the values in this dataset.
```{r}
image(volcano)
```

You can also render plot with a main title, using `main`:

```{r pressure, echo=FALSE}
plot(pressure, main="A non-descriptive title")
```

- Useful **bookmark 1**: Find more tips on using R Markdown on the [full tutorial](https://finetut.com/lessons/introduction-to-rmarkdown-r-notebook)!  
- Useful **bookmark 2**: Find more tips on working with Markdown on the [full tutorial](https://finetut.com/lessons/working-with-markdown-document/)!  


